Fermi and eROSITA bubbles

### 2021-12-16 paper.tex
update

  We model the external and fixed gravity of the Milky Way by prescribing a\
  plane parallel self-gravitating isothermal slab, symmetry about the mid-plane $z=0$,\
  in a simulation box size of\
  $14\times14\times28$ kpc, slightly larger than the size of eROISTA bubbles.

@@

  where $\Phi_{\text{halo}}=v^2_{\text{halo}}\ln\left(z^2+d^2_{\text{h}}\right)$\

  is dark logarithmic halo potential,

@@

  is the potential of a plane-parallel isothermal slab.

  The slab is used to mimic the gravity contributed by the stars within the Galactic plane,\
  the  thus

  We mimic the galactic potential by using

  The potential of slab is mainly contributed by the stars within the Galactic center.

@@

  We use three components (1) cold ISM disk (2) hot gas ambient (3) stellar disk\
  to locally mimic the environment near the GC (i.e. no galactic rotation).\

  The density distributions of ISM disk and hot gas ambient are derived from\
  hydrostatic equilibrium within the fixed external potential.

  We use the potential of isothermal slab, symmetric about $z=0$, and\
  supported by gas pressure and by its own self-gravity,\
  to mimic the realistic potential of Galactic bulge.

>>>>

  We model the external gravity of the Milky Way by prescribing a\
  plane parallel self-gravitating isothermal slab, symmetry about the mid-plane $z=0$,\
  in a simulation box size of\
  $14\times14\times28$ kpc, slightly larger than the size of eROISTA bubbles.

@@

  where $\Phi_{\text{halo}}=v^2_{\text{halo}}\ln\left(z^2+d^2_{\text{h}}\right)$\
  is dark logarithmic halo potential,

@@

  is the potential of a plane-parallel isothermal slab contributed by stars within the Galactic plane.

  The steady-state density distribution in a total potential, $\Phi_{\text{total}}$,\
  for the atmosphere gas can be derived from the isothermal and hydrostatic equilibrium condition,\
  given by

  \begin{equation}
     \rho(z)=
     \begin{cases}
     \displaystyle\rho_{\text{atmp}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{atmp}}/m}\right] & \text{if z > $z_{0}$}\\
     \displaystyle\rho_{\text{disk}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{disk}}/m}\right] & \text{if z > $z_{0}$}
     \end{cases}
  \end{equation}

  where $\rho_{\text{atmp}}^{\text{peak}}$ can be obtained by assuming that pressure\
  and gravitational potential are continuous at the interface ($z=\pm z_{0}$) between disk and atmosphere.

@@

  The adopted parameters for are

  %We use three components (1) cold ISM disk (2) hot gas ambient (3) stellar disk\
  %to locally mimic the environment near the GC (i.e. no galactic rotation).\

  %The density distributions of ISM disk and hot gas ambient are derived from\
  %hydrostatic equilibrium within the fixed external potential.

  %We use the potential of isothermal slab, symmetric about $z=0$, and\
  %supported by gas pressure and by its own self-gravity,\
  %to mimic the realistic potential of Galactic bulge.
